\documentclass[a4paper]{article}
\title{\huge{\textsc{Personal Statement}}}
\author{Nishant Rai}
\date{}
\usepackage[margin=2cm]{geometry}
\usepackage{caption}
\usepackage{amsmath}
\usepackage[export]{adjustbox}
\usepackage{enumerate}
\usepackage{url}
\usepackage{authblk}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{setspace}
\usepackage{mdframed}
\usepackage{booktabs}
\usepackage{ragged2e}

\begin{document}

	\maketitle	
	
	I am a \textbf{Third-year undergraduate} student pursuing a B. Tech. in the department of \textbf{Computer Science And Engineering} at the \textbf{Indian Institute of Technology, Kanpur, India}. I am applying for an internship at The Computational Vision and Geometry Lab (CVGL) at Stanford for Summers '16.\\

When I first enrolled in college I was clueless about the vastness of the world of computer science. Thus, to find my fields which really interest me, I've worked on many projects which made me interested in problems related to Algorithms, Machine Learning and Computer Vision. I have done a research internship at \textbf{INRIA Paris} last summer related to \textbf{Road Networks} and \textbf{Social Networks} which introduced me to the beautiful area of research. I have also completed a research internship at \textbf{Xerox Research Centre India} (related to \textbf{Multi View Clustering}). The work has also been submitted in \textbf{IJCAI-16} and is currently under review. We also plan on submitting the work on Alternate Paths in \textbf{ESA-16 (European Symposium On Algorithms)}.\\

\textbf{Algorithms} was my first love, the beauty of algorithms fascinates me till date. I became interested in it when I started competitive programming. I believe it's due to the problem/puzzle solver inside of me. I've always been amazed by facing new problems and trying to think about their solutions. I did a project related to \textbf{geometric data structures} which involved re inventing solutions to problems in the field (Like Simplex query). It involved use of topics such as Ham sandwich cuts, Convex Onions, Convex hulls, etc and helped me reaffirm my love for algorithms. I also completed a project related to road networks and Social Networks later.\\

\textbf{Machine Learning} and \textbf{Computer Vision} are my \textbf{current} favorites. I started becoming interested in it during my first year project : \textbf{News Report Classification} and \textbf{Multimodal Emotion Recognition}. I have taken a graduate level course in \textbf{Natural Language Processing} , in which I completed a project related to \textbf{“Unsupervised computation of Mulitple Sense Embeddings”}. I'm currently taking graduate level courses, \textbf{Machine Learning: Tools and Techniques} and \textbf{Computer Vision and Image Processing}, both of which involve a project component. For the ML course, the project I'm working on is \textbf{"Real Time Vehicle Tracking and License Plate Recognition"}. I am extremely interested in doing more projects in the field to help me learn more about it. I try to keep myself updated with advances in the field and have implemented algorithms such as Mean Shift Based Image Segmentation and Interest Point Based Matching.\\

I am extremely confident in my \textbf{programming skills}; First, due to the large variety of projects I've completed; Second, due to my active participation in programming contests which involve fast coding skills. I'm proficient in multiple programming languages and libraries such as \textbf{C++, Python, MATLAB, Octave} and \textbf{Java} (Familiar).\\

As mentioned in my CV, I have earlier been selected for taking part in the \textbf{International Mathematics Olympiad training Camp} – 2013 as a \textbf{senior member}, which is only offered to a select few students from the country (\textbf{6 overall}). It also requires clearing earlier stages, during which I secured \textbf{first} position in my region. I love maths and have some confidence in my  mathematical background, I believe it's very helpful in problems related to ML, Algorithms and those requiring rigorous analysis. I had also been selected for the \textbf{International Physics Olympiad Training Camp}, which again requires clearing some stages and is only offered to a few students. I am also interested in competitive programming, a sort of coding sport (or contests) which require solving tough algorithmic problems in a short amount of time. My CV contains prizes I have received in such contests, which further shows my love for solving problems. As mentioned earlier, I have also completed many projects under Professors and Clubs. \\

These are some of the reasons due to which I feel I can live up to your expectations. But the biggest reason according to me is the will to learn, persevere and work hard, which I believe I can do. If I am given the opportunity to do an internship at the CVGL Lab, I will surely give it my all and not betray your confidence in me. \\

\end{document}


