\documentclass[a4paper]{norm-resume} % Use US Letter paper, change to a4paper for A4 

\usepackage{array}
\usepackage{tabularx}
\usepackage{setspace}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Nishant}{Rai}{home.iitk.ac.in/~nishantr}{nishantr@iitk.ac.in}

\vspace{2mm}

% Education section : With current and previous schooling

\section{Education}
		
\begin{tabularx}{\textwidth}{c l l r}	
	{April 2017 \hspace{10mm}} & B.Tech \emphasize{(Computer Science And Engineering)} \hspace{22mm} & \emphasize{IIT Kanpur \hspace{10mm}} & {\textbf{{9.9/10.0}}}\\		
	{April 2013 \hspace{10mm}} & Class XII \emphasize{(Central Board for Senior Education)} & \emphasize{K.V. Delhi} & {\textbf{{96.20 \%}}}\\
	{April 2011 \hspace{10mm}} & Class X \emphasize{(Central Board for Senior Education)} & \emphasize{K.V. Shillong} & {\textbf{{10.0/10.0}}}\\	
\end{tabularx}

\vspace{1mm}	% Some space before next section

% Academic Acheivements

\section{Academic Achievements}

\vspace{3mm} %Some space
		
\begin{tightitemize}
	\item Received \textbf{Charpak Research Scholarship} for the year \textbf{2015}.
	\item Received the \textbf{Academic Excellence Award} for exceptional academic performance in the \textbf{13-14} academic session.
	\item Secured AIR - \textbf{257} in {\textbf{JEE (Advanced) 2013}} and AIR - {\textbf{79}} in \textbf{JEE (Mains) 2013}.
	\item One amongst the \textbf{6 INMO Awardees} selected for \textbf`{IMO training camp}, after clearing \textbf{INMO '13}.
	\item Awarded Gold medal for being selected for \textbf{IPhO training camp}, after clearing \textbf{INPhO '13}.
	\item Awarded \textbf{Ashray Hasta Award and Scholarship, 2013} for exceptional performance in \textbf{AISSCE, 2013}.
	\item Selected for the prestigious \textbf{KVPY} scholarship, in stream SX.
	\item Secured \textbf{Rank 1} in \textbf{Regional Mathematics Olympiad '12} (Delhi Region).	
\end{tightitemize}
	
\vspace{0mm}	% Some space before next section

% Programming Acheivements

\section{Achievements in Programming}

\vspace{3mm} %Some space

\begin{tightitemize}
	\item Secured \textbf{1\textsuperscript{st}} place in \textbf{Microsoft CodeHunt} amongst individuals from over the country. Selected for \textbf{finals} in \textbf{China}.
	\item Secured \textbf{13\textsuperscript{th}} place in \textbf{IOPC} (International Online Programming Contest) amongst \textbf{900+} teams from over the world held during \textbf{Techkriti '15}.
	\item Secured \textbf{1\textsuperscript{st}} place in the event \textbf{Chaos} (Esoteric Programming Contest) held during \textbf{Techkriti '15}
	\item Secured \textbf{17\textsuperscript{th}} place in in \textbf{Morgan Stanley Codeathon 2014} amongst \textbf{1000+} individuals from over the country.
	\item Secured \textbf{26\textsuperscript{th}} place in \textbf{ACM ICPC Onsite Contest} 2014 amongst \textbf{250+} teams from over the country.
	\item Secured \textbf{1\textsuperscript{st}} place in the \textbf{Web-dev} event during \textbf{Takneek '14} (Inter-Hostel Technical Competition).
	\item Secured \textbf{1\textsuperscript{st}} place in the programming event \textbf{Blackbox} during \textbf{Takneek '13} (Inter-Hostel Technical Competition).
\end{tightitemize}

\vspace{0mm}	% Some space before next section

% Internships

\section{Internships}

\vspace{2mm} %Some space
		
\runsubsection{X.R.C.I}				\descript{Research Internship}
\duration{Xerox Research Center India}{Dec '15}
\location{Bangalore, India}

\vspace{-1mm} %Reduce some space

	\begin{changemargin}{1.0cm}{0.0cm} 
	{
	\large{\bgemph{Multi View Clustering via Non Negative Matrix Factorization:}}  \\
	\small{Mentored by \lgemph{Om Deshmukh, Senior Researcher} (Area Manager, Multimedia Analytics), \lgemph{XRCI} and \lgemph{Sumit Negi, Principal Researcher, XRCI}, for developing and evaluating algorithms for Multi View Clustering using Non Negative Matrix factorization.} 		
	}
	\end{changemargin} 	
	
	\vspace{1mm}
	
\runsubsection{I.N.R.I.A.}				\descript{Research Internship}
\duration{The French Institute for Research in Computer Science and Automation}{May '15 - Jul '15}
\location{Rocquencourt, France}
	
\vspace{-1mm} %Reduce some space

	\begin{changemargin}{1.0cm}{0.0cm} 
	{
	\large{\bgemph{Alternate Paths in Road networks:}}  \\
	\small{Mentored by \lgemph{Laurent Viennot, Senior Researcher, INRIA} and \lgemph{Adrian Kosowski, Researcher, INRIA}, for finding routes substantially different from the shortest path based on different criteria.} 
	\begin{tightitemize}
	\small
	{
	\item Implemented various shortest path algorithms and compared their efficiency on real world road networks.
	\item Proposed algorithms to compute paths according to another feasible definition.
	\item Created measures to compare different algorithms developed efficient algorithms for the involved computations.
	\item \textbf{Algorithms Involved:} \textbf{Dijkstra search, Floyd Warshall algorithm, A* search, Bidirectional Search, Landmark based search, Reach based pruning, Contraction hierarchies, K shortest Paths} and \textbf{Alternate Graphs}.
	}
	\end{tightitemize}
	
\vspace{1mm} %Some space	
			
	\large{\bgemph{Feature Based Representation of Social Networks:}} \\
	\small{Mentored by \lgemph{Adrian Kosowski, Researcher, INRIA} with an aim to good local features which can act as suitable predictors for the graph's global features.}
	\begin{tightitemize}
	\small
	{
	\item Studied information spread models and about maximizing spread, Local Ranking problem, Pagerank algorithm. 
	\item Implemented and studied randomized rumor spreading, the relation between size and steps for spread of the rumor
	\item Studied and explored different local features in graphs based on walks, subgraph densities, centrality measures and their relation with other global properties along with arguments to explain the obtained results.
	\item \textbf{Topics involved:} \textbf{Models of Information Spread In Networks, Maximizing Information spread (using Initial Partial Incentives), PageRank Algorithm, Similarity of graphs/nodes, Local ranking problem} and \textbf{Randomised rumor spreading}.
	}
	\end{tightitemize}
 	
	}
	\end{changemargin} 	

\vspace{0mm}	% Some space before next section

% Details about the projects

\section{Projects}

\vspace{2mm} %Some space

	\runsubsection{Word Embeddings with Multiple Word prototypes:}				\descript{Aug '15 - Nov '15}	
	\begin{tightitemize}
	\small
	{
	\item \textbf{Course Project} for course \textbf{CS671A}: Introduction to Natural Language Processing, under \textbf{Prof. Amitabha Mukherjee}.
	\item Project aimed at constructing of \textbf{Multiple Sense Embeddings} for different words using purely \textbf{unsupervised approaches}.
	\item Proposed algorithms involved \textbf{Online clustering}, analysis of Word-Word \textbf{co-occurrence matrix} and \textbf{Non-parametric clustering} using penalties based on Negative Sampling.
	\item \textbf{Outperform existing methods} in Local Similarity Metric and comparable in terms of other metrics, result in more semantically coherent senses than the state of the art methods.
	\item \textbf{Techniques Used:} \textbf{Low Dimensional Word embeddings, Negative Sampling, Online Clustering, Word Sense disambiguation, X Means, Cuthill Mckee ordering} and \textbf{Semantic Similarity}.
	}
	\end{tightitemize}
		
	\vspace{2mm}

	\runsubsection{NachOS Operating System:}   \descript{July '15 - Nov '15}
	\begin{tightitemize}
	\small
	{
	\item \textbf{Course Project} for course \textbf{CS330A}: Operating Systems, under \textbf{Prof. Mainak Chaudhuri}.
	\item \textbf{Extended} the \textbf{NachOS} operating system to perform basic operating system functions including \textbf{Fork, Join, Sleep} and \textbf{Exec}. 
	\item Implemented and evaluated performance of various algorithms for scheduling processes.
	\item Developed and added support for \textbf{Demand Paging, Shared Memory, Condition Variables} and \textbf{Semaphores}.	
	}
	\end{tightitemize}
		
	\vspace{2mm}
	
	\runsubsection{Multi Modal Emotion Recognition:}   \descript{May '14 - Jun '14}
	\begin{tightitemize}
	\small
	{
	\item Project aimed at performing \textbf{Emotion Detection} using three features i.e. \textbf{textual, speech} and \textbf{visual}. Developed emotion detectors which use text, video and audio as features.
	\item Merged the results of the three classifiers to identify emotions accurately.
	\item \textbf{Techniques Used:} \textbf{Support Vector Machines, Neural Networks, Randomised Forest Classifiers, Decision Trees, K Nearest Neighbours, Hidden Markov Models, Image Normalisation, Noise reduction, PCA} and \textbf{POS Tagging}.
	\item Learnt about \textbf{Facial Action Coding System,
Active Shape/Appearance Models} and other prevalent methods for emotion classification.
	}
	\end{tightitemize}
		
	\vspace{2mm}
	
	\runsubsection{Geometric Data Structures:}   \descript{Sep '14 - Nov '14}
	\begin{tightitemize}
	\small
	{
	\item Project for \textbf{Advanced Track} in course \textbf{CS210}: Data Structures and Algorithms, under \textbf{Prof. Surendar Baswana}.
	\item Project involved re-invention of several geometric data structures to efficiently answer specified queries.	
	\item \textbf{Queries handled:} \textbf{Point in Polygon, Convex Hull, Polygon-Line intersection, Simplex problem, Orthogonal Range Search} and \textbf{Half Plane problem}.
	}
	\end{tightitemize}
 		
	\vspace{2mm}
		
	\runsubsection{News Report Classification:}   \descript{Jan '14 - Apr '14}
	\begin{tightitemize}
	\small
	{
	\item Project aimed at \textbf{classifying news articles} into categories, implemented \textbf{K Nearest Neighbors} and \textbf{automated scraping} of online news articles.
	\item \textbf{Techniques Used (NLP):} \textbf{Tokenisation, Lemmatisation, TFID, Stopword removal} and \textbf{Bernoulli Models}.
	\item \textbf{Techniques Used (ML):} \textbf{Support Vector Machines, Naive Bayes Classifier, K-Nearest neighbours} and \textbf{Neural Networks}
	}
	\end{tightitemize}
 		
	\vspace{2mm}
	
	\runsubsection{Sentiment Analysis of Social Media:}   \descript{Aug' 14}
	\begin{tightitemize}
	\small
	{
	\item Application developed during \textbf{Web-Dev, Takneek '14} and secured \textbf{First} position.
	\item Interface to analyze the past and present \textbf{social sentiment of brands} and \textbf{their products}, identify "good" and "bad" features of the product.
	}
	\end{tightitemize}
 		
	\vspace{2mm}
	
	\runsubsection{Mechanical Object Elevator:}  	\descript{Aug '14 - Nov '14}
	\begin{tightitemize}
	\small
	{
	\item Awarded \textbf{Best Sectional Project} in course \textbf{TA201}: Manufacturing Processes - I.
	\item Demonstrated the use of \textbf{CAM} Mechanism in elevating objects using periodic rotational motion.
	}
	\end{tightitemize}
 	
	\vspace{2mm}
	
	\runsubsection{Other Minor Projects:}
	\begin{tightitemize}
	\small
	{
	\item Implemented a \textbf{Captcha Decoder}, able to work with some level of noise.
	\item Created models for \textbf{Predicting Search trends}, \textbf{Assigning Topic} based on keywords and \textbf{Categorizing questions} into multiple classes.
	\item Completed project to discover patterns and trends about the \textbf{New York Subway}, under the \textbf{Udacity} course: \textbf{Intro to Data Science}.
	}
	\end{tightitemize}		

\vspace{2mm}	% Some space before next section

% Skills

\section{Technical Skills}

\vspace{2mm}	% Some space

\category{\large{Programming Languages} \small\scshape(Proficient):} \hfill \emphasize{C, C++, Python, MatLab, GNU Octave, Assembly (Verilog)} \\
\vspace{1mm}	%Some Space
\category{\large{Programming Languages} \small\scshape(Familiar):} \hfill \emphasize{Java, CSS, JavaScript, PHP, MySQL} \\
\vspace{1mm}	%Some Space
\category{\large{Software and Utilities:}} \hfill \emphasize{Git, GNUPlot, \LaTeX\, AUTOCAD Inventor}

\vspace{0mm}	% Some space before next section

% Positions of Responsibility

\section{Positions of Responsibility}

\vspace{2mm} %Some space
		
	\begin{tabular}{r|p{16cm}}	
	
	\null \hspace{10mm} \normalsize\emph{Jan '15 - Current} & \textbf{Member, Core Team Academics, Counseling Service}\\
	& \small{Responsible for managing remedial lectures, mentor allotment and other academics related issues.}\\
	& \small{Managing a team of 100+ Academic Mentors to help and guide academically troubled students.}\\
	& \small{Assisting peer students in departmental courses by conducting classes as well as personal tutoring.}\\

	\multicolumn{2}{c}{} \\
	\normalsize\emph{Aug '14 - Mar '15} & \textbf{Senior Executive, Public Relations, Techkriti '15, IIT Kanpur}\\
	& \small{Responsible for inviting eminent personalities for talks, shows and looking after their publicity and hospitality}\\
	& \small{Responsible for smooth conduction of 5 talks and 2 shows in the festival along with other teammates.}\\
	& \small{Managed a team of 15 members to organise TechPlanet which witnessed footfall of over 3000 people}	\\

	\multicolumn{2}{c}{} \\
	\normalsize\emph{Apr '14 - Apr '15} & \normalsize\textbf{Secretary, Programming Club}\\

	\normalsize\emph{Jun '14 - Apr '15} & \normalsize\textbf{Academic Mentor (MTH101/102), Counselling Service}\\ 

	\normalsize\emph{Jun '14 - Apr '15} & \normalsize\textbf{Student Guide, Counselling Service}\\

	\normalsize\emph{Previous} & \normalsize\textbf{Secretary, Hospitality Cell, Udghosh '14}\\
	
	& \normalsize\textbf{Volunteer, Hospitality Cell, Udghosh '13}\\

	\end{tabular}

\vspace{0mm}	% Some space before next section

% Interests

\section{Interests}

\vspace{2mm} %Some space

	{\large{
	{Algorithms and Data Structures \hfill Artificial Intelligence \\
	Competitive Programming\hfill Computer Vision\\
	Machine Learning \hfill Natural Language Processing\\}		
	}}

\vspace{2mm}	% Some space before next section

% Relevant Courses

\section{Relevant Courses}

\vspace{2mm} %Some space
		
\begin{small}
	\begin{tabularx}{\textwidth}{X X l}
	{\textbf{ESC101} : Fundamentals of Computing} & {\textbf{MTH101} : Analytical Calculus} &{\textbf{MTH102} : Linear Algebra and DE}\\
	{\textbf{CS201} : Discrete Mathematics}&{\textbf{CS210 }: Data Structures and Algorithms} & {\textbf{Coursera}: Algorithms }\\
	{\textbf{Udacity}: Intro to Data Science } & {\textbf{CS251} : Computing Laboratory} &{\textbf{CS202} : Mathematical Logic} \\ 
	{\textbf{CS203} : Abstract Algebra} & {\textbf{CS220} : Computer Organization} & {\textbf{MSO201} : Probability and Statistics}\\
	{\textbf{CS345} : Algorithms - II}&{\textbf{CS330} : Operating Systems}&{\textbf{CS340} : Theory of Computation}\\
	{\textbf{CS252} : Computing Laboratory - II}&{\textbf{CS671} : Natural Language Processing} &{\textbf{CS771} : Machine Learning *}\\
	{\textbf{CS676} : \footnotesize{Computer Vision and Image Processing *}}&{\textbf{CS335} : Compiler Design *}
	& {\hfill \footnotesize\emphasize{* - Next Semester}}\\
	\end{tabularx}
\end{small}	

\vspace{2mm}	% Some space before next section

% Relevant Courses

\section{Extra-Curricular Activities}

\vspace{2mm} %Some space
	
	Secured \textbf{1\textsuperscript{st}} place in \textbf{Reviews} - Lifestyle event in \textbf{Spectrum '14} (Inter-Hostel Competition).\\
	Secured \textbf{1\textsuperscript{st}} place in \textbf{Tennis (Singles)} in \textbf{Freshers' Inferno '13} (Inter-Hostel Sports Competition).\\	
	Selected for \textbf{CBSE Tennis Regionals} (Guwahati Region), 2009.\\
	Selected for participation in \textbf{U-17 Inter School Table-Tennis Tournament}, Shillong in 2010.\\
	Secured \textbf{1\textsuperscript{st}} place in \textbf{U-17 Tennis Open} held at Basava International School, New Delhi in 2011.\\

\end{document}